FoRTE baseline

### 2019-07-02 analysis/paper/paper.Rmd
Drop confidence intervals, color ensembles in summary plot

```{r summary-ts-plot, fig.cap = summary_ts_cap, fig.dim = c(10, 7)}
summary_ts_cap <- paste(
  htmlfig(),
  "ED2 plot-level ensemble predictions of",
  "gross (GPP) and net (NPP) primary productivity,",
  "total leaf area index (LAI), and aboveground biomass (AGB)",
  "by model configuration.",
  "Individual ensemble members are shown as gray lines.",
  "The solid line is a LOESS regression (`ggplot2::stat_smooth`).",
  "Shading represents the middle 80% (10th to 90th percentile) of predictions.",
  "Black dot with error bars is the mean and min/max value",
  "from Hardiman et al. (2013)."
)
readd(summary_ts_plot)
```

>>>>

```{r summary-ts-plot, fig.cap = summary_ts_cap, fig.dim = c(10, 10)}
summary_ts_cap <- paste(
  htmlfig(),
  "ED2 plot-level predictions of",
  "gross (GPP) and net (NPP) primary productivity,",
  "aboveground biomass (AGB),",
  "total leaf area index (LAI),",
  "and Shannon diversity index (of plant functional types)",
  "by model configuration.",
  "The solid line is the ensemble mean.",
  "Black dot with error bars is the mean and min/max value",
  "from Hardiman et al. (2013)."
)
readd(summary_ts_plot)
```
